A thesis draft

### 2018-11-19 res/sections/08-Background.tex
Fix spaces
Fix sentences

\section{Network slicing}
A network slice can be defined as a logical virtual network, tailored for a
given use case, on the top a common network using technologies such as
Software-Defined Networking and Network Function Chaining that allows network
softwarization~\cite{ordonez2017network}. The notion of separated virtual
networks deployed on the same infrastructure is not new, e.g. VPN, but it has
some specifics that make it a novel idea. The concept of network slicing was
first introduced in 2002 with the in\cite{peterson2003blueprint}, where
is described an overlay network that allows services to access different slices
of overlay's resources and in which overlay management services run in their
own slice. Lately this idea has be refined  and
in\cite{alliance2016description} the design of network slicing was based on a
three-layers model, as depicted in
Figure~\ref{chap:background:img:network_slicing}.

>>>>

\section{Network slicing}
A network slice can be defined as a logical virtual network, tailored for a
given use case, on the top a common network using technologies such as
Software-Defined Networking and Network Function Chaining that allows network
softwarization~\cite{ordonez2017network}. The notion of separated virtual
networks deployed on the same infrastructure is not new, e.g. VPN, but it has
some specifics that make it a novel idea. The concept of network slicing was
first introduced in 2002 in\cite{peterson2003blueprint}, where a network 
overlay is illustrated, allowing services to run continuously and to access the 
overlay resources across different slices. Services operating over the overlay 
management have their own slice instead. This idea was lately refined in 2016, 
where the design of network slicing was based on a three-layers 
model~\cite{alliance2016description}, as depicted in 
Figure~\ref{chap:background:img:network_slicing}.
